\documentclass[11pt]{article}
\thispagestyle{empty}
\usepackage[none]{hyphenat}
% ---------- Packages ----------
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{titlesec}

\usepackage{fancyhdr}
\pagestyle{fancy}

\fancyhf{}                % clear all header/footer
\fancyhead[R]{\small \thepage}   % page number on top right
\fancyhead[L]{\small \it Soham Jana}
\renewcommand{\headrulewidth}{0pt} % remove header line


% ---------- Formatting ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\hypersetup{
	colorlinks=true,
	urlcolor=blue
}

\setlist[itemize]{noitemsep, topsep=2pt}
\setlist[enumerate]{noitemsep, topsep=4pt}

\begin{document}
	
	% ---------- Header ----------
	{\Huge \textbf{Soham Jana}} \\[4pt]
	Assistant Professor, University of Notre Dame \\
	Department of Applied and Computational Mathematics and Statistics \\
	Email: \href{mailto:sjana2@nd.edu}{sjana2@nd.edu} \quad
	Website: \href{https://janasoham.github.io}{janasoham.github.io}\\
	Phone: +1 574-631-5503 \quad Office: 101 E Crowley Hall
	
	\vspace{6pt}
	
	% ---------- Research ----------
	\section*{Research Interests}
	Theoretical and methodological aspects of high-dimensional statistics, neural networks, mixture modeling, distance-based estimators.
	
	% ---------- Education ----------
	\section*{Education}
	\textbf{Ph.D. in Statistics and Data Science}, Yale University \hfill 2022 \\
	Advisor: Yihong Wu \\
	Thesis: Learning non-parametric and high-dimensional distributions via information-theoretic methods
	
	\textbf{Master of Statistics (First class with distinction)}, Indian Statistical Institute \hfill 2017 \\
	Specialization: Theoretical Statistics \\
	Dissertation: Characterization of single-integral non-kernel divergences \\
	Advisor: Ayanendranath Basu
	
	\textbf{Bachelor of Statistics (First class with distinction)}, Indian Statistical Institute \hfill 2015
	
	% ---------- Employment ----------
	\section*{Employment}
	\textbf{University of Notre Dame} \hfill 2024--Present \\
	Assistant Professor, Department of Applied and Computational Mathematics and Statistics
	
	\textbf{Princeton University} \hfill 2022--2024 \\
	Postdoctoral Researcher, Department of Operations Research and Financial Engineering \\
	Hosts: Sanjeev Kulkarni, Jianqing Fan
	
	Researcher, First Republic Bank Research and Lifelong Learning Program \hfill 2022--2023
	
	Lecturer \hfill Spring 2023, Fall 2023
	
	% ---------- Grants ----------
	\section*{Grants and Awards}
	Kaneb Center Course Design Academy, University of Notre Dame \hfill 2024--2025 \\
	Award Amount: \$5000
	
	% ---------- Publications ----------
	\section*{Publications}
	{\small * Authors not in alphabetical order \quad $^\dagger$ Equal contribution}
	
	\subsection*{Journal Publications}
	\begin{enumerate}
		
		\item \textbf{Jana, S.}, Yang, K., \& Kulkarni, S. (2026).* \\
		Adversarially robust clustering with optimality guarantees. \\
		\textit{IEEE Transactions on Information Theory}, 72(1), 478--500.
		
		\item \textbf{Jana, S.}, Polyanskiy, Y., \& Wu, Y. (2025). \\
		Optimal empirical Bayes estimation for the Poisson model via minimum-distance methods. \\
		\textit{Information and Inference}, Volume 14, Issue 4.
		
		\item \textbf{Jana, S.}, Fan, J., \& Kulkarni, S. (2025).* \\
		A provable initialization and robust clustering method for general mixture models. \\
		\textit{IEEE Transactions on Information Theory}, vol. 71, no. 9.
		
		\item \textbf{Jana, S.}, Li, H., Yamada, Y., \& Lindenbaum, O. (2023). \\
		Support recovery with stochastic gates: theory and application for linear models. \\
		\textit{Signal Processing}, 213.
		
		\item Han, Y., \textbf{Jana, S.}, \& Wu, Y. (2023). \\
		Optimal prediction of Markov chains with and without spectral gap. \\
		\textit{IEEE Transactions on Information Theory}, 69(6).
		
		\item \textbf{Jana, S.}, \& Basu, A. (2019).* \\
		A characterization of all single-integral, non-kernel divergence estimators. \\
		\textit{IEEE Transactions on Information Theory}, 65(12).
		
	\end{enumerate}
	
	\subsection*{Conference Publications}
	\begin{enumerate}
		
		\item \textbf{Jana, S.}, Polyanskiy, Y., Teh, A., \& Wu, Y. (2023). \\
		Empirical Bayes via ERM and Rademacher complexities: the Poisson model. \\
		\textit{Conference on Learning Theory (COLT)}, PMLR 195:5199--5235.
		
		\item Han, Y., \textbf{Jana, S.}, \& Wu, Y. (2021). \\
		Optimal prediction of Markov chains with and without spectral gap. \\
		\textit{Neural Information Processing Systems (NeurIPS)}.
		
		\item \textbf{Jana, S.}, Polyanskiy, Y., \& Wu, Y. (2020). \\
		Extrapolating the profile of a finite population. \\
		\textit{Conference on Learning Theory (COLT)}.
		
	\end{enumerate}
	
	\subsection*{Preprints}
	\begin{enumerate}
		
		\item Xing, H.$^\dagger$, \textbf{Jana, S.}$^\dagger$, \& Maleki, A. (2025).* \\
		Minimax analysis of estimation problems in coherent imaging. \\
		arXiv:2508.18503.
		
		\item Fan, J., \textbf{Jana, S.}, Kulkarni, S., \& Yin, Q. (2025). \\
		Factor informed double deep learning for average treatment effect estimation. \\
		arXiv:2508.17136.
		
		\item Chen, X.$^\dagger$, \textbf{Jana, S.}$^\dagger$, Metzler, C., Maleki, A., \& Jalali, S. (2025).* \\
		Multilook coherent imaging: theoretical guarantees and algorithms. \\
		arXiv:2505.23594.
		
		\item Tang, S., \textbf{Jana, S.}, \& Fan, J. (2024). \\
		Factor adjusted spectral clustering for mixture models. \\
		Under major revision at \textit{Journal of the American Statistical Association}.
		
	\end{enumerate}
	
	% ---------- Talks ----------
	\section*{Conferences, Workshops, and Invited Talks}
	\begin{itemize}
		\item Statistical Learning and Data Science: Inference and Intelligence, New York, USA (November 2026)
		\item World Meeting of the International Society for Bayesian Analysis, Nagoya, Japan (June 2026)
		\item IMSI Workshop on Reinforcement Learning from Offline Data and Human Feedback, Chicago, USA (April 2026)
		\item Joint Statistical Meetings, Nashville, TN, USA (August 2025)
		\item IMS New Researchers Conference, Nashville, TN, USA (July--August 2025)
		\item International Webinar on Recent Trends in Statistical Theory and Applications, Kerala, India (July 2025)
		\item International Indian Statistical Association, Lincoln, NE, USA (June 2025)
		\item International Indian Statistical Association, Cochin, Kerala, India (December 2024)
		\item Joint Statistical Meetings, Portland, OR, USA (August 2024)
		\item University of Notre Dame Statistics Department Seminar, Notre Dame, IN, USA (February 2024)
		\item University of Wisconsin--Madison Statistics Department Seminar, Madison, WI, USA (February 2024)
		\item University of Texas at Dallas Statistics Department Seminar, Richardson, TX, USA (January 2024)
		\item Indian Statistical Institute ISRU Department Seminar, Kolkata, India (July 2023)
		\item Conference on Learning Theory (COLT), Bangalore, India (July 2023)
		\item Neural Information Processing Systems (NeurIPS), Virtual (December 2021)
		\item Conference on Learning Theory (COLT), Graz, Austria (July 2020)
	\end{itemize}
	
	% ---------- Teaching ----------
	\section*{Teaching}
	
	\textbf{University of Notre Dame}
	\begin{itemize}
		\item ACMS 30530 -- Introduction to Probability (Fall 2024, 2025, Spring 2026)
		\item ACMS 70100 -- Machine Learning Methods for High-dimensional Data (Spring 2026)
		\item ACMS 80870 -- Modern Machine Learning Techniques with Application (Spring 2025)
	\end{itemize}
	
	\textbf{Princeton University}
	\begin{itemize}
		\item ORF 309/ENG 309/MAT 380 -- Probability and Stochastic Systems (Spring 2023)
		\item ORF 570 -- Statistical Machine Learning (Fall 2023)
	\end{itemize}
	
	% ---------- Service ----------
	\section*{Professional Service}
	Paper reviews (29): Annals of Statistics (3), Journal of the American Statistical Association (2), IEEE Transactions on Information Theory (5), Journal of the Royal Statistical Society (2), IEEE Wireless Communications Letters (1), IEEE ISIT (1), Electronic Journal of Statistics (2), Stat (1), Algorithmic Learning Theory (7), Bernoulli (1), Statistica Sinica (1), Journal of Statistical Planning and Inference (1), Biometrics (1), SIAM Journal on Mathematics of Data Science (1).
	
	% ---------- Organization ----------
	\section*{Conference Organization}
	\begin{itemize}
		\item CFE-CMStatistics Conference (December 2025): Session organizer -- Recent advances in Causal Inference
		\item Joint Statistical Meetings (August 2025): Session chair -- New Advances in Optimization Algorithms for Causal Discovery
		\item Joint Statistical Meetings (August 2024): Session chair -- New Advances in Nonparametric Hypothesis Testing - Part I
		\item Joint Statistical Meetings (August 2024): Session chair -- New Developments in Non-Euclidean Statistics
		\item IEEE Conference on Information Sciences and Systems (March 2024): Session chair -- Machine learning and statistical inference
	\end{itemize}
	
	% ---------- Community ----------
	\section*{Community Service}
	\begin{itemize}
		\item Teaching at Math Circle, Notre Dame (Spring 2025, Fall 2025): Promoting STEM education among school children
	\item Yale S\&DS M.A. admission committee (2021): handled 150+ applications
	\item Yale S\&DS graduate reading group (2020): co-organizer
	\item Yale Women in Data Science (WiDS) workshop (2020): mentor
	\item South Asian Graduate and Professional Association (SAGA), Yale (2018--2021): Treasurer and organizer
	\end{itemize}
	
	% ---------- Awards ----------
	\section*{Other Awards}
	INSPIRE Scholarship, Government of India (2012--2017) \\
	INMO Merit Certificate (Top 75, 2012)
	
\end{document}